Codebook

### 2020-01-06 codebook.Rmd
no actual edits to anything, just file changes caused by me linking the repository to a second machine with a different system

```{r prepare_codebook}
library(codebook)
library(readxl)
library(here)
library(rio)

codebook_data <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", n_max = 243)
#Read codebook from second sheet in excel file.
dict <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "codebook")

#Add variable labels to data
var_label(codebook_data) <- dict_to_list(dict)
val_labels(codebook_data$include_in_analysis) <- c("excluded" = 0, "included" = 1)
val_labels(codebook_data$is_RR) <- c("CR" = 0, "RR"= 1)
val_labels(codebook_data$support_binary) <- c("no support" = 0, "partial or full support" = 1)
val_labels(codebook_data$is_replication) <- c("is not a replication" = 0, "is a replication" = 1)
val_labels(codebook_data$contains_replic) <- c("does not contain 'replic'" = 0, "contains 'replic'" = 1)
val_labels(codebook_data$hyp_from_fulltext) <- c("hypothesis from abstract alone" = 0, "hypothesis from full text" = 1)
val_labels(codebook_data$result_from_fulltext) <- c("result from abstract alone" = 0, "result from full text" = 1)
val_labels(codebook_data$coding_round) <- c("RR pilot" = 0,
                                            "main coding round" = 1,
                                            "CR replacements and late RR additions" = 2,
                                            "second CR replacement" = 3)
val_labels(codebook_data$uses_AS_coding) <- c("uses MS coding" = 0, "uses AS coding" = 1)
val_labels(codebook_data$coded_by_MS) <- c("not coded by MS" = 0, "coded by MS" = 1)
val_labels(codebook_data$evaluation_certainty_MS) <- c("not certain" = 1,
                                                       2,
                                                       3,
                                                       4,
                                                       "very certain" = 5)
val_labels(codebook_data$hypothesis_from_fulltext_MS) <- c("hypothesis from abstract alone" = 0, "hypothesis from full text" = 1)
val_labels(codebook_data$result_from_fulltext_MS) <- c("result from abstract alone" = 0, "result from full text" = 1)
val_labels(codebook_data$fulltext_available_MS) <- c("full text not available" = 0, "full text available" = 1)
val_labels(codebook_data$is_replication_old_MS) <- c("does not contain a replication" = 0, "contains a replication" = 1)
val_labels(codebook_data$is_original_old_MS) <- c("does not contain original work" = 0, "contains original work" = 1)
val_labels(codebook_data$coded_by_AS) <- c("not coded by AS" = 0, "coded by AS" = 1)
val_labels(codebook_data$evaluation_certainty_AS) <- c("not certain" = 1,
                                                       2,
                                                       3,
                                                       4,
                                                       "very certain" = 5)
val_labels(codebook_data$hypothesis_from_fulltext_AS) <- c("hypothesis from abstract alone" = 0, "hypothesis from full text" = 1)
val_labels(codebook_data$result_from_fulltext_AS) <- c("result from abstract alone" = 0, "result from full text" = 1)
val_labels(codebook_data$fulltext_available_AS) <- c("full text not available" = 0, "full text available" = 1)
val_labels(codebook_data$is_replication_old_AS) <- c("does not contain a replication" = 0, "contains a replication" = 1)
val_labels(codebook_data$is_original_old_AS) <- c("does not contain original work" = 0, "contains original work" = 1)
val_labels(codebook_data$is_replication_new_coded_by_AS) <- c("replication status not coded by AS" = 0, "replication status coded by AS" = 1)
val_labels(codebook_data$is_replication_new_AS) <- c("is not a replication" = 0, "is a replication" = 1)
val_labels(codebook_data$is_replication_new_coded_by_DL) <- c("replication status not coded by DL" = 0, "replication status coded by DL" = 1)
val_labels(codebook_data$is_replication_new_DL) <- c("is not a replication" = 0, "is a replication" = 1)
val_labels(codebook_data$is_replication_special_issue) <- c("not part of replication special issue" = 0, "part of replication special issue" = 1)
val_labels(codebook_data$hypothesis_intro_contains_replic) <- c("hypothesis intro does not contain 'replic'" = 0, "hypothesis intro contains 'replic'" = 1)

#Add meta data
metadata(codebook_data)$name <- "Positive Results in Registered Reports in Psychology"
metadata(codebook_data)$description <- "Coded variables to compare the proportion of papers that find support for their first tested hypothesis between Registered Reports and conventional reports in psychology"
metadata(codebook_data)$creator <- "Anne Scheel, Mitchell Schijen, Daniël Lakens"
metadata(codebook_data)$temporalCoverage <- "Winter 2018"

>>>>

```{r prepare_codebook}
library(codebook)
library(readxl)
#library(here)
library(rio)

codebook_data <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", n_max = 243)

# Read codebook from second sheet in Excel file.
dict <- read_excel("positive_results_in_registered_reports_masterfile_data.xlsx", sheet = "codebook")

# Add variable labels to data (from Excel file)
var_label(codebook_data) <- dict_to_list(dict)

# Add value labels to data (manually)
val_labels(codebook_data$include_in_analysis) <- c("excluded" = 0, "included" = 1)
val_labels(codebook_data$is_RR) <- c("SR" = 0, "RR"= 1)
val_labels(codebook_data$support_binary) <- c("no support" = 0, "partial or full support" = 1)
val_labels(codebook_data$is_replication) <- c("is not a replication" = 0, "is a replication" = 1)
val_labels(codebook_data$contains_replic) <- c("does not contain 'replic'" = 0, "contains 'replic'" = 1)
val_labels(codebook_data$hyp_from_fulltext) <- c("hypothesis from abstract alone" = 0, "hypothesis from full text" = 1)
val_labels(codebook_data$result_from_fulltext) <- c("result from abstract alone" = 0, "result from full text" = 1)
val_labels(codebook_data$coding_round) <- c("RR pilot" = 0,
                                            "main coding round" = 1,
                                            "SR replacements and late RR additions" = 2,
                                            "second SR replacement" = 3)
val_labels(codebook_data$uses_AS_coding) <- c("uses MS coding" = 0, "uses AS coding" = 1)
val_labels(codebook_data$coded_by_MS) <- c("not coded by MS" = 0, "coded by MS" = 1)
val_labels(codebook_data$evaluation_certainty_MS) <- c("not certain" = 1,
                                                       2,
                                                       3,
                                                       4,
                                                       "very certain" = 5)
val_labels(codebook_data$hypothesis_from_fulltext_MS) <- c("hypothesis from abstract alone" = 0, "hypothesis from full text" = 1)
val_labels(codebook_data$result_from_fulltext_MS) <- c("result from abstract alone" = 0, "result from full text" = 1)
val_labels(codebook_data$fulltext_available_MS) <- c("full text not available" = 0, "full text available" = 1)
val_labels(codebook_data$is_replication_old_MS) <- c("does not contain a replication" = 0, "contains a replication" = 1)
val_labels(codebook_data$is_original_old_MS) <- c("does not contain original work" = 0, "contains original work" = 1)
val_labels(codebook_data$coded_by_AS) <- c("not coded by AS" = 0, "coded by AS" = 1)
val_labels(codebook_data$evaluation_certainty_AS) <- c("not certain" = 1,
                                                       2,
                                                       3,
                                                       4,
                                                       "very certain" = 5)
val_labels(codebook_data$hypothesis_from_fulltext_AS) <- c("hypothesis from abstract alone" = 0, "hypothesis from full text" = 1)
val_labels(codebook_data$result_from_fulltext_AS) <- c("result from abstract alone" = 0, "result from full text" = 1)
val_labels(codebook_data$fulltext_available_AS) <- c("full text not available" = 0, "full text available" = 1)
val_labels(codebook_data$is_replication_old_AS) <- c("does not contain a replication" = 0, "contains a replication" = 1)
val_labels(codebook_data$is_original_old_AS) <- c("does not contain original work" = 0, "contains original work" = 1)
val_labels(codebook_data$is_replication_new_coded_by_AS) <- c("replication status not coded by AS" = 0, "replication status coded by AS" = 1)
val_labels(codebook_data$is_replication_new_AS) <- c("is not a replication" = 0, "is a replication" = 1)
val_labels(codebook_data$is_replication_new_coded_by_DL) <- c("replication status not coded by DL" = 0, "replication status coded by DL" = 1)
val_labels(codebook_data$is_replication_new_DL) <- c("is not a replication" = 0, "is a replication" = 1)
val_labels(codebook_data$is_replication_special_issue) <- c("not part of replication special issue" = 0, "part of replication special issue" = 1)
val_labels(codebook_data$hypothesis_intro_contains_replic) <- c("hypothesis intro does not contain 'replic'" = 0, "hypothesis intro contains 'replic'" = 1)

# Add meta data
metadata(codebook_data)$name <- "Positive Results in Registered Reports in Psychology"
metadata(codebook_data)$description <- "Coded variables to compare the proportion of papers that find support for their first tested hypothesis between Registered Reports and standard reports in psychology"
metadata(codebook_data)$creator <- "Anne Scheel, Mitchell Schijen, Daniël Lakens"
metadata(codebook_data)$temporalCoverage <- "Winter 2018"
